Examining the Multifaceted Impact of Family Size on Happiness, Health, Gender Dynamics, and Financial Well-being

### 2023-04-04 outputs/paper/paper.qmd
Add files via upload

---
title: "Exploring Relationships between Demographic Characteristics, Health, Finances, Living Arrangements, and Happiness"
subtitle: "An Analysis of the General Social Survey (GSS) Data from 1972 to 2012"
author: 
  - SHAOHAN CHANG
thanks: "Code and data are available at: https://github.com/lucas11333/Factor_of_Wellbeing"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This paper presents an analysis of a subset of the General Social Survey (GSS) data from the year 1972, which includes information on individuals' demographic characteristics, health, finances and subjective well-being. The study aimed to explore various aspects of individuals' lives during the early 1970s in the United States, such as social stratification, gender roles, family dynamics, health disparities, and subjective well-being.The dataset consists of 13 observations and 24947 variables, for example: including year, age, sex, babies, divorce, health, finance satisfied and happy. The study used graphical representation to analyze the relationships between different variables in the dataset and individuals' level of happiness. The results of the analysis suggest that there is a positive relationship between people's satisfaction with their current financial situation, their self-rated health, and their level of happiness in life. Additionally, being divorced may have a slight impact on one's level of happiness in life, with a small proportion of individuals feeling not too happy. Moreover, the study found that people's level of education is positively associated with their level of happiness in life, as people's education level increases, their level of happiness also gradually increases.Overall, this study provides valuable insights into various aspects of individuals' lives during the early 1970s in the United States. The findings can be useful for researchers and students interested in exploring topics such as social stratification, gender roles, family dynamics, health disparities, and subjective well-being. The study highlights the importance of considering different factors that can influence individuals' level of happiness and well-being, such as their financial situation, health status, and level of education. Further research could investigate more recent data from the GSS to examine changes in these relationships over time."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Surveys are a common method for collecting data on individuals' attitudes, behaviors, and experiences in social science research. One such survey is the General Social Survey (GSS), which has been conducted in the United States since 1972 to 2012. This data set is a subset of the GSS data from the year 1972, which includes information on individuals' demographic characteristics, health, finances and subjective well-being. While this is a relatively small data set, it provides a glimpse into the lives of individuals in the United States during a particular period in time.This paper aims to explore various aspects of individuals' lives during the early 1970s in the United States using the GSS data set. The variables in this data set are diverse and reflect a range of aspects of individuals' lives. For instance, the variables on babies and divorce provide information on individuals' family structures, while the variables on health and finance satisfaction offer insights into their well-being and financial stability [@b]. The data set also includes variables on individuals' living arrangements and their subjective well-being, providing a glimpse into their social context and overall happiness.

The paper presents a comprehensive analysis of the relationships between different variables in the data set and individuals' level of happiness. The analysis includes a graphical representation of the relationship between the number of children and happiness in the family, individuals' self-rated health and their self-rated level of happiness, people's satisfaction with their financial situation and their happiness, the level of happiness in life for individuals in two different states: divorced or married, and the relationship between people's level of education and their level of happiness in life.The results of the analysis suggest that there is a positive relationship between people's satisfaction with their current financial situation, their self-rated health, and their level of happiness in life [@a]. The analysis also indicates that being divorced may have a slight impact on one's level of happiness in life, with a small proportion of individuals feeling "not too happy." Additionally, as people's education level increases, their level of happiness also gradually increases.

Overall, this paper provides valuable insights into various aspects of individuals' lives during the early 1970s in the United States. The findings can be useful for researchers and students interested in exploring topics such as social stratification, gender roles, family dynamics, health disparities, and subjective well-being.

@@

## Data {#sec-data}

@@

This data-set contains information on various personal and demographic characteristics of individuals, collected between the years 1972 and 2012. The data-set includes variables such as age, sex, number of babies, divorce status, self-reported health status, financial satisfaction and level of happiness. The data-set can be used to study the relationships between these variables and to gain insights into factors that may influence an individual's overall life satisfaction.

```{r}
#| eval: true
#| warning: false
#| echo: false
data %>%
  select(1:8) %>%
  slice(1:5) %>%
  kable(caption = "Table of Happy by Various Variables") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

@@

```{r}
#| eval: true
#| warning: false
#| echo: false
#| label: table-one
#| table-cap: Report Data (First 5 rows)

data %>%
  select(9:13) %>%
  slice(1:5) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

```{r}
#| eval: true
#| warning: false
#| echo: false
data %>%
  select(14:15) %>%
  slice(1:5) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

-   year: This variable indicates the year in which the data was collected. In this data-set, all the observations are from the year 1972 to 2012.
-   age: This variable indicates the age of the individual at the time the data was collected. It is a continuous variable measured in years.
-   sex: This variable indicates the biological sex of the individual. It is a categorical variable with two levels: male and female.
-   babies: This variable indicates the number of babies the individual had at the time the data was collected. It is a categorical variable with different levels, depending on the number of babies: 0, 1, 2, 3, 4, or 5+.
-   divorce: This variable indicates whether or not the individual had ever been divorced at the time the data was collected. It is a categorical variable with two levels: yes and no.
-   health: This variable indicates the self-reported health status of the individual at the time the data was collected. It is a categorical variable with different levels, depending on the health status: excellent, good, fair, or poor.
-   finance_satisfied: This variable indicates the individual's level of satisfaction with their current financial situation. It is a categorical variable with different levels of satisfaction: very satisfied, more or less satisfied, not very satisfied, and not at all satisfied.
-   happy: This variable indicates the individual's level of happiness or life satisfaction. It is a categorical variable with different levels of happiness: very happy, pretty happy, not too happy, and not at all happy.
-   divorce_score: This variable is a binary representation of the divorce status of an individual in the dataset. The value '0' denotes that the individual is not divorced, while the value '1' indicates that they are divorced.
-   happy_score: The happy_score variable is an ordinal variable representing the self-reported happiness levels of the individuals in the dataset. It ranges from 0 to 3, with 0 representing "not too happy," 1 representing "happy," 2 representing "very happy," and 3 reserved for any unclassified or missing responses.
-   degree_score: This ordinal variable represents the educational attainment of the individuals in the dataset. It ranges from 1 to 5, where 1 signifies "less than high school," 2 denotes "high school," 3 represents "associate/junior college," 4 refers to "bachelor's," and 5 indicates "graduate" level education. The value 6 is reserved for any unclassified or missing responses.
-   health_score: The health_score variable is an ordinal variable indicating the self-reported health status of the individuals in the dataset. It ranges from 1 to 4, with 1 denoting "poor" health, 2 signifying "fair" health, 3 representing "good" health, and 4 referring to "excellent" health. The value 5 is reserved for any unclassified or missing responses.
-   finance_score: This ordinal variable represents the financial satisfaction level of the individuals in the dataset. It ranges from 1 to 3, with 1 indicating "Not at all satisfied," 2 denoting "more or less satisfied," and 3 signifying "pretty well satisfied." The value 4 is reserved for any unclassified or missing responses.
-   babies_number: The babies_number variable is an ordinal variable denoting the number of babies an individual in the dataset has. It ranges from 0 to 4, where 0 represents "0" babies, 1 denotes "1" baby, 2 signifies "2" babies, 3 indicates "3" babies, and 4 refers to "4" babies. The value 5 is reserved for any unclassified or missing responses.

In [@fig-one], this chart shows the number of people who are very happy, not too happy, and happy. Overall, the data indicates that the largest number of people are happy, with approximately 15,000 individuals falling into this category. On the other hand, the smallest number of people are not too happy, with significantly fewer individuals in this category compared to the other two variables. In summary, the data suggests that the number of unhappy individuals is a relatively small group.

### Analyzing the Impact of Family Size on Happiness

```{r}
#| label: fig-one
#| fig-cap: Couning of Happiness
#| echo: false
#| warning: false

ggplot(data, aes(x = happy, fill = happy)) +
  geom_bar() +
  scale_fill_manual(values = c("#FFC107", "#FF5722", "#4CAF50", "#2196F3")) +
  labs(fill = "Happiness level")+
  coord_flip()

@@

In [@fig-two], through the graph showing the relationship between the number of children and happiness in the family, it is obvious that when people have no children, the largest number of 'very happy', 'pretty happy', and 'not too happy' are shown. Although The preliminary judgment is that the number of people who are happy without children is the largest. But among the data, the data collected without children is the most. In order to ensure the accuracy of the data, it is necessary to further analyze the proportion of the number of children in the family for the next part of the analysis.

```{r}
#| label: fig-two
#| fig-cap: Relationship between Number of Babies and Happiness
#| echo: false
#| warning: false

data %>% 
  filter(babies != "unknown") %>% 
  group_by(babies, happy) %>% 
  summarize(n = n()) %>% 
  mutate(prop = n / sum(n)) %>% 
  ggplot(aes(x = factor(babies), y = prop, group = happy, color = happy)) +
  geom_line(size = 1.5) +
  stat_smooth(geom = "ribbon", alpha = 0.2) +
  scale_x_discrete(name = "Number of Babies", expand = c(0.1, 0.1)) +
  scale_y_continuous(labels = scales::percent_format(), name = "Percentage", expand = c(0.05, 0)) +
  scale_color_discrete(name = "Happiness") +
  theme_minimal() +
  theme(plot.title = element_text(size = 16, face = "bold", margin = margin(b = 10)),
        plot.subtitle = element_text(size = 14, margin = margin(b = 20)),
        axis.title = element_text(size = 12, face = "bold"),
        axis.text = element_text(size = 10),
        legend.title = element_text(size = 12, face = "bold"),
        legend.text = element_text(size = 10),
        legend.position = "bottom")

@@

### The Interplay of Health and Happiness: Evaluating the Link Between Self-Perceived Health and Life Satisfaction

In [@fig-four], which represents the relationship between participants' self-rated health and their self-rated level of happiness. The chart shows that the proportion of participants who rated themselves as "very happy" was the highest among those who rated their health as "excellent". On the other hand, the proportion of participants who rated themselves as "not too happy" was the lowest among those who rated their health as "poor".From the overall trend, it can be inferred that the higher the participants' self-rated health, the higher their self-rated level of satisfaction with life.

```{r}
#| label: fig-four
#| fig-cap: Relationship between Health and Happiness
#| echo: false
#| warning: false
ggplot(data, aes(x = health, fill = happy)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Health", y = "Percentage of Happy Cases") +
  theme_minimal() +
  coord_flip()
```

In [@fig-five], which spanning from 1970 to 2010, illustrates the relationship between participants' self-reported happiness levels and their health states. It is evident that when participants rated their health as 'poor', the proportion of those who identified as 'very happy' was notably lower compared to other health states. On the other hand, when participants reported their health as 'excellent' or 'good', the number of 'very happy' responses regarding their life satisfaction increased significantly. In summary, this chart suggests a positive correlation between people's health and their happiness in life.

```{r}
#| label: fig-five
#| fig-cap: Relationship between Health and "Very Happy" With Year
#| echo: false
#| warning: false
ggplot(data[data$happy == "very happy", ], aes(x = year, y = health)) +
  geom_point(position = position_jitter(width = 0.2, height = 0.1), size = 2, color = "#4daf4a") +
  facet_wrap(~health, ncol = 5, scales = "free_y") +
  labs(x = "Year", y = "Self-rated Health") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.major.x = element_line(color = "grey", size = 0.1),
        strip.text = element_text(size = 10),
        panel.spacing = unit(0.2, "lines"))

@@

### The Financial Satisfaction-Happiness

In [@fig-six], the graph depicts the relationship between people's satisfaction with their financial situation and their happiness.It is clear that when people are not very satisfied with their current finances, the proportion of unhappy people in their lives is the highest. On the other hand, when people are very satisfied with their finances, the proportion of happy people in their lives is the highest, and the proportion of unhappy people is also the lowest. Therefore, it can be concluded that there is a positive relationship between people's satisfaction with their current financial situation and their level of happiness in life.

```{r}
#| label: fig-six
#| fig-cap: Relationship between Happiness and finance satified
#| echo: false
#| warning: false
#| 
ggplot(data, aes(x = finance_satified, fill = happy)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Rate of Finance Satified ",
       y = "Percentage of Happy Cases") +
  theme_minimal() +
  coord_flip()
```

### Marital Status and Happiness: Comparing the Emotional Well-Being of Married and Divorced Individuals

In [@fig-seven], the graph represents the level of happiness in life for individuals in two different states: divorced or married. The graph shows that the levels of happiness in both marital states are almost similar. However, the proportion of people who feel "not too happy" in their lives is slightly higher among the divorced group than among the married group. In conclusion, being divorced may have a slight impact on one's level of happiness in life, with a small proportion of individuals feeling "not too happy."

```{r}
#| label: fig-seven
#| fig-cap: Relationship between Happiness and Divorce
#| echo: false
#| warning: false
ggplot(data, aes(x = divorce, fill = happy)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Divorce",
       y = "Percentage of Happy Cases") +
  theme_minimal() +
  coord_flip()

In [@fig-eight], which based on the analysis of the charts, it appears that for the years 1972, 1975, 1982, 1990, 1996, 2002, and 2010, individuals who reported being divorced also reported a higher percentage of happy responses. On the other hand, for the years 1976, 1980, 1984, 1987, 1989, and 2006, individuals who reported being married reported a higher percentage of happy responses. Additionally, the percentage of individuals who reported "not too happy" was significantly higher for individuals who reported being divorced than for those who reported being married in the years 1973, 1984, 1987, 1990, 1991, 1993, 2008, and 2012.

```{r fig.width= 8,fig.height= 4}
#| label: fig-eight 
#| fig-cap: Relationship between Divorce and Happiness by Year
#| echo: false
#| warning: false
data %>%
  filter(divorce != "unknown") %>%
  group_by(year, divorce, happy) %>%
  summarize(n = n()) %>%
  mutate(prop = n / sum(n)) %>%
  ggplot(aes(x = factor(divorce), y = prop, group = happy, color = happy)) +
  geom_line(size = 1.5) +
  stat_smooth(geom = "ribbon", alpha = 0.2) +
  facet_wrap(~ year, nrow = 2) +
  scale_x_discrete(name = "Divorce", expand = c(0.1, 0.1)) +
  scale_y_continuous(labels = scales::percent_format(), name = "Percentage", expand = c(0.05, 0)) +
  scale_color_discrete(name = "Happiness") +
  theme_minimal() +
  theme(plot.title = element_text(size = 16, face = "bold", margin = margin(b = 10)),
        plot.subtitle = element_text(size = 14, margin = margin(b = 20)),
        axis.title = element_text(size = 12, face = "bold"),
        axis.text = element_text(size = 10),
        legend.title = element_text(size = 12, face = "bold"),
        legend.text = element_text(size = 10),
        legend.position = "bottom")

### Education and Emotional Well-Being

In [@fig-nine], which shows that there is a certain relationship between people's level of education and their level of happiness in life. From the graph, it can be observed that the proportion of people who feel "not too happy" is the highest among those with education levels lower than high school. However, the proportion of unhappy individuals is the lowest among those with bachelor's and graduate degrees, suggesting that as people's education level increases, their level of happiness also gradually increases.

```{r}
#| label: fig-nine
#| fig-cap: Relationship between Happiness and Degree
#| echo: false
#| warning: false
ggplot(data, aes(x = degree, fill = happy)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Degree",
       y = "Percentage of Happy Cases") +
  theme_minimal() +
  coord_flip()

@@

$$
\hat{Y}=\hat{\beta_0}+\hat{\beta_1}X_{age}+\hat{\beta_2}X_{degree-score}+\hat{\beta_3}X_{finance-score}+\hat{\beta_4}X_{health-score} + \hat{\beta_5}X_{divorce-score} + 
\hat{\beta_6}X_{babies-number}
$$ {#eq-model}

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: tbl-lm
#| tbl-cap: Linear Model and its Summary Statistics
model <- lm(data$happy_score ~ age +  degree_score + finance_score + health_score + divorce_score + babies_number, data=data)

modelsummary :: modelsummary(
  list(
    "Well-Being" = model
  ),
  fmt = 2,
  statistic = "conf.int"
)
```

In @eq-model:

-   ${\hat{Y}}$ is predicted value of the dependent variable. This is the outcome we're trying to predict or estimate based on the independent variables.
-   ${\hat{\beta_0}}$ : The intercept term, which represents the expected value of ${\hat{Y}}$ when all independent variables are equal to 0.
-   ${\hat{\beta_1}}$ , ${\hat{\beta_2}}$ , ${\hat{\beta_3}}$ , ${\hat{\beta_4}}$ , ${\hat{\beta_5}}$ and ${\hat{\beta_6}}$ are the estimated coefficients for each independent variable. These coefficients indicate the average change in the dependent variable ${\hat{Y}}$ associated with a one-unit change in the corresponding independent variable, holding all other variables constant. The independent variables are:
-   $X_{age}$ : Age of the individual.
-   $X_{degree-score}$ : A measure of the individual's level of education or degree.
-   $X_{finance-score}$ : A measure of the individual's financial stability or status.
-   $X_{health-score}$ : A measure of the individual's overall health.
-   $X_{divorce-score}$ : A measure of the individual's likelihood of divorce or past divorces.
-   $X_{babies-number}$ : The number of babies/children the individual has.

The purpose of this multiple linear regression model is to understand the relationship between these independent variables and the dependent variable. By fitting the model to a dataset, we can estimate the coefficients and make predictions for new observations. we can also use the model to identify which independent variables have the most significant impact on the dependent variable and determine the strength and direction of those relationships.The [@tbl-lm], which is based the equation of @eq-model :

-   Overall model significance: The F-statistic (314.461) indicates that the overall model is statistically significant, suggesting that the predictors included in the model collectively explain a meaningful portion of the variance in well-being.
-   Model fit: The R-squared (0.070) and adjusted R-squared (0.070) values are relatively low, indicating that only 7% of the variation in well-being is explained by the predictors in the model. This suggests that there may be other factors influencing well-being that have not been included in the model.
-   Age as a predictor: The coefficient for age (0.00) and its confidence interval (\[0.00, 0.00\]) suggest that age does not have a statistically significant effect on well-being in this model.
-   Degree score as a predictor: The positive coefficient for degree_score (0.02) and its confidence interval (\[0.01, 0.03\]) indicate that higher degree scores are associated with higher well-being. This suggests a positive relationship between educational achievement and well-being.
-   Finance score as a predictor: The negative coefficient for finance_score (−0.09) and its confidence interval (\[−0.11, −0.08\]) demonstrate that higher finance scores are associated with lower well-being. This indicates a negative relationship between financial stress and well-being.
-   Health score as a predictor: The positive coefficient for health_score (0.32) and its confidence interval (\[0.30, 0.34\]) show that higher health scores are associated with higher well-being. This suggests a strong positive relationship between health and well-being.
-   Divorce score as a predictor: The coefficient for divorce_score (−0.02) and its confidence interval (\[−0.05, 0.01\]) indicate that the effect of divorce_score on well-being is not statistically significant. This suggests that the relationship between divorce and well-being is inconclusive in this model.
-   Number of babies as a predictor: The negative coefficient for babies_number (−0.03) and its confidence interval (\[−0.05, −0.01\]) demonstrate that having more babies is associated with lower well-being. This indicates a negative relationship between the number of children and well-being.

In conclusion of this result, the model shows that degree_score, finance_score, health_score, and babies_number are statistically significant predictors of well-being, while age and divorce_score are not. However, the low R-squared value suggests that there are likely other factors affecting well-being that have not been included in the model.

@@

## Table of Relationship between Number of Children and Happiness in the Family.

In the table two, which appears to be presenting data on the happiness levels of babies, as rated by some measure or criteria, at different ages from 0 to 4 years old. The three categories of happiness levels are "not too happy," "happy," and "very happy." Looking at the data for 4-year-old, we can see that 48.15% of them were rated as "not too happy," 14.81% as "very happy," and the remaining 37.04% as simply "happy." This suggests that the majority of 4-year-old were not rated as particularly happy, with less than half of them falling into the happy or very happy categories.

>>>>

---
title: "Examining the Multifaceted Impact of Family Size on Happiness, Health, Gender Dynamics, and Financial Well-being"
subtitle: ""
author: 
  - SHAOHAN CHANG
thanks: "Code and data are available at: https://github.com/lucas11333/Of_Wellbeing"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This study analyzed the relationship between family size, measured by the number of children, and various aspects of family life, such as happiness, health, and financial satisfaction. The findings suggest that happiness levels are highest among childless individuals, while families with one child report the best health status. Additionally, higher financial satisfaction is associated with fewer children in a family. These insights matter as they provide a better understanding of the factors influencing family size and the potential consequences of family planning decisions on overall wellbeing."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

The impact of the number of children in a family on various aspects of family life has been a topic of interest for researchers and policymakers alike [@a]. Family size and structure play a crucial role in shaping the lives of individuals and communities. Understanding the connections between the number of children and factors such as happiness, health, sex distribution, and financial satisfaction can help inform decisions and policies aimed at promoting family well being [@b]. This paper seeks to explore these relationships and shed light on the complex interplay between family size and various aspects of family life.

The paper examines the relationship between the number of children (0, 1, 2, 3, 4) in a family and different variables such as happiness, health, sex distribution, and financial satisfaction using multiple data sources. Previous research on this topic has often focused on specific aspects of family life or specific sub populations, leaving a gap in the understanding of the broader relationships between family size and different variables. This study aims to fill this gap by providing a comprehensive analysis of the relationship between the number of children in a family and various aspects of family life.

Through the analysis of several charts and tables, this study uncovers patterns and trends in the data that suggest connections between the number of children in a family and the variables of interest. For example, the data reveals that families with better health tend to have a higher likelihood of having one or more children, while families with lower financial satisfaction tend to have more children [@c]. However, the relationships identified in this study may not be linear, and it is important to consider the potential influence of other factors on the number of children in a family.

The structure of the paper is as follows: first, we present the data and methodology used in the study, followed by a detailed analysis of the relationships between the number of children in a family and the variables of interest. Next, we discuss the implications of the findings and their relevance to broader discussions on family well being and policy. Finally, we conclude with a summary of the main findings and suggestions for future research in this area.

@@

## Data

@@

In @tbl-var contains information on various personal and demographic characteristics of individuals, collected between the years 1972 and 2012. The data-set includes variables such as age, sex, number of babies, divorce status, self-reported health status, financial satisfaction and level of happiness. The data-set can be used to study the relationships between these variables and to gain insights into factors that may influence an individual's overall life satisfaction.

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: tbl-var
#| tbl-cap: Report Data (First 5 rows)
data %>%
  select(1:6) %>%
  slice(1:5) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

@@

```{r}
#| echo: false
#| warning: false
data %>%
  select(6:10) %>%
  slice(1:5) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

-   year: This variable indicates the year in which the data was collected. In this data-set, all the observations are from the year 1972 to 2012.
-   sex: This variable indicates the biological sex of the individual. It is a categorical variable with two levels: male and female.
-   babies: This variable indicates the number of babies the individual had at the time the data was collected. It is a categorical variable with different levels, depending on the number of babies: 0, 1, 2, 3, 4, or 5+.
-   health: This variable indicates the self-reported health status of the individual at the time the data was collected. It is a categorical variable with different levels, depending on the health status: excellent, good, fair, or poor.
-   finance_satisfied: This variable indicates the individual's level of satisfaction with their current financial situation. It is a categorical variable with different levels of satisfaction: very satisfied, more or less satisfied, not very satisfied, and not at all satisfied.
-   happy: This variable indicates the individual's level of happiness or life satisfaction. It is a categorical variable with different levels of happiness: very happy, pretty happy, not too happy, and not at all happy.
-   happy_score: The happy_score variable is an ordinal variable representing the self-reported happiness levels of the individuals in the dataset. It ranges from 0 to 3, with 0 representing "not too happy," 1 representing "happy," 2 representing "very happy," and 3 reserved for any unclassified or missing responses.
-   health_score: The health_score variable is an ordinal variable indicating the self-reported health status of the individuals in the dataset. It ranges from 1 to 4, with 1 denoting "poor" health, 2 signifying "fair" health, 3 representing "good" health, and 4 referring to "excellent" health. The value 5 is reserved for any unclassified or missing responses.
-   finance_score: This ordinal variable represents the financial satisfaction level of the individuals in the dataset. It ranges from 1 to 3, with 1 indicating "Not at all satisfied," 2 denoting "more or less satisfied," and 3 signifying "pretty well satisfied." The value 4 is reserved for any unclassified or missing responses.
-   babies_number: The babies_number variable is an ordinal variable denoting the number of babies an individual in the dataset has. It ranges from 0 to 4, where 0 represents "0" babies, 1 denotes "1" baby, 2 signifies "2" babies, 3 indicates "3" babies, and 4 refers to "4" babies. The value 5 is reserved for any unclassified or missing responses.

In [@fig-one],which analysis of this data is to calculate the number of children with 0, 1, 2, 3, 4.through the graph showing the relationship between the number of children and happiness in the family, it is obvious that when people have no children, the largest number of 'very happy', 'pretty happy', and 'not too happy' are shown. Although The preliminary judgment is that the number of people who are happy without children is the largest. But among the data, the data collected without children is the most. In order to ensure the accuracy of the data, it is necessary to further analyze the proportion of the number of children in the family for the next part of the analysis.

```{r}
#| label: fig-one
#| fig-cap: Relationship between Number of Babies and Happiness
#| echo: false
#| warning: false
data %>%
  group_by(babies, happy) %>%
  summarize(n = n()) %>%
  mutate(prop = n / sum(n)) %>%
  ggplot(aes(x = factor(babies), y = prop, fill = happy)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_x_discrete(name = "Number of Babies", expand = c(0.1, 0.1)) +
  scale_y_continuous(labels = scales::percent_format(), name = "Percentage", expand = c(0.05, 0)) +
  scale_fill_discrete(name = "Happiness") +
  theme_minimal() +
  theme(plot.title = element_text(size = 16, face = "bold", margin = margin(b = 10)),
        plot.subtitle = element_text(size = 14, margin = margin(b = 20)),
        axis.title = element_text(size = 12, face = "bold"),
        axis.text = element_text(size = 10),
        legend.title = element_text(size = 12, face = "bold"),
        legend.text = element_text(size = 10),
        legend.position = "bottom")

@@

In [@fig-two],which presented in the table indicates that the sex distribution varies depending on the number of babies in the family. A higher percentage of females compared to males is consistently observed across all groups. The lowest difference in sex distribution is found among families with no babies, where the female-to-male ratio is relatively closer. As the number of babies in a family increases, the percentage of females also increases, with the highest difference observed in families with one and four babies. In these groups, the sex distribution is more skewed towards females.

```{r}
#| label: fig-two
#| fig-cap: Relationship between Number of Babies and Gender
#| echo: false
#| warning: false
data %>%
  group_by(babies, sex) %>%
  summarize(n = n()) %>%
  mutate(prop = n / sum(n)) %>%
  ggplot(aes(x = factor(babies), y = prop, fill = sex)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_x_discrete(name = "Number of Babies", expand = c(0.1, 0.1)) +
  scale_y_continuous(labels = scales::percent_format(), name = "Percentage", expand = c(0.05, 0)) +
  scale_fill_discrete(name = "Sex") +
  theme_minimal() +
  theme(plot.title = element_text(size = 16, face = "bold", margin = margin(b = 10)),
        plot.subtitle = element_text(size = 14, margin = margin(b = 20)),
        axis.title = element_text(size = 12, face = "bold"),
        axis.text = element_text(size = 10),
        legend.title = element_text(size = 12, face = "bold"),
        legend.text = element_text(size = 10),
        legend.position = "bottom")

@@

### The Relationship Between Number of Children and Self-Rated Health Status

In [@fig-four], the analysis of the chart, it can be observed that when individuals have one child, there is a significantly higher proportion of participants who rate their health as 'good' or 'excellent' compared to other categories. In contrast, for participants who do not have any children, the proportion of those who rate their health as 'poor' is the highest, but no clear conclusion can be drawn from this finding. For individuals with three children, the feedback on their health status is evenly distributed among 'good', 'fair', and 'excellent', with a very small proportion of participants reporting 'poor' health. Overall, having one child is associated with the highest proportion of participants reporting 'excellent' health status.

```{r}
#| label: fig-four
#| fig-cap: Number of Children and Self-Rated Health Status
#| echo: false
#| warning: false

ggplot(data, aes(x = health, fill = factor(babies))) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Health", y = "Percentage of Cases by Number of Babies", fill = "Number of Babies") +
  theme_minimal() +
  coord_flip()
```

In [@fig-five], which present the dot plot, which represent the each number of babies in different condition of health, which explores the relationship between health and the number of babies in the family. The data is organized into four health categories - 'excellent', 'fair', 'good', and 'poor' - and five categories based on the number of babies, ranging from 0 to 4.The data reveals a pattern suggesting a connection between health status and the number of babies in a family. Families with 'excellent' health have a more balanced distribution of babies, with a higher proportion of families having one or two babies compared to those with poorer health. This trend indicates that better health is associated with a higher likelihood of having one or more babies.As the number of babies increases, the percentages for all four health categories tend to decrease. This pattern is most noticeable in the 'poor' health category, where the decline in percentages is more pronounced as the number of babies increases.In summary, the data suggests a relationship between health and the number of babies in a family. Better health is generally associated with a higher likelihood of having one or more babies, while poorer health tends to correlate with a lower likelihood. However, it is essential to consider that the relationship may not be linear and that other factors could also influence the number of babies in a family.

```{r}
#| label: fig-five
#| fig-cap: Relationship between Health and Number of Babies With Year
#| echo: false
#| warning: false

ggplot(data[data$happy == "very happy", ], aes(x = year, y = factor(babies))) +
  geom_point(position = position_jitter(width = 0.2, height = 0.1), size = 2, color = "#4daf4a") +
  facet_wrap(~health, ncol = 5, scales = "free_y") +
  labs(x = "Year", y = "Number of Babies") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.major.x = element_line(color = "grey", size = 0.1),
        strip.text = element_text(size = 10),
        panel.spacing = unit(0.2, "lines"))

@@

### The Association Between Family Size and Financial Satisfaction

In [@fig-six], which appears that the number of babies in a family is related to the level of financial satisfaction. In general, families with lower financial satisfaction, regardless of the category, tend to have a higher number of babies. This trend is observed across all three financial satisfaction levels.It is interesting to note that the majority of families in all financial satisfaction levels have 0 babies. However, the percentage of families with 0 babies is notably higher in the 'pretty well satisfied' category compared to the 'more or less satisfied' and 'not satisfied at all' categories.As the number of babies increases, the percentages for all three financial satisfaction categories tend to decrease. This pattern is more pronounced in the 'pretty well satisfied' category, where the decline in percentages is steeper as the number of babies increases.In summary, the data suggests a connection between financial satisfaction and the number of babies in a family. Families with higher financial satisfaction generally have fewer babies, while those with lower financial satisfaction have more babies. It is essential to consider that this relationship may not be linear, and other factors could also influence the number of babies in a family.

```{r}
#| label: fig-six
#| fig-cap: Relationship between Happiness and finance satified
#| echo: false
#| warning: false
ggplot(data, aes(x = finance_satified, fill = factor(babies))) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Rate of Finance Satisfaction",
       y = "Percentage of Cases by Number of Babies",
       fill = "Number of Babies") +
  theme_minimal() +
  coord_flip()

@@

$$
\hat{Y}=\hat{\beta_0}+\hat{\beta_1}X_{finance-score}+\hat{\beta_2}X_{health-score} + \hat{\beta_3}X_{happy} + 
\hat{\beta_6}X_{babies-number} 
$$ {#eq-model}

```{r}
#| message: false
#| echo: false
#| warning: false    
#| label: tbl-lm
#| tbl-cap: Linear Model and its Summary Statistics
model <- lm(data$babies ~  finance_score + health_score + happy, data=data)

modelsummary :: modelsummary(
  list(
    "Babies" = model
  ),
  fmt = 2,
  statistic = "conf.int"
)
```

The @tbl-lm is built based on the @eq-model:

-   ${\hat{Y}}$ is predicted value of the dependent variable. This is the outcome we're trying to predict or estimate based on the independent variables.
-   ${\hat{\beta_0}}$ : The intercept term, which represents the expected value of ${\hat{Y}}$ when all independent variables are equal to 0.
-   ${\hat{\beta_1}}$ , ${\hat{\beta_2}}$ , ${\hat{\beta_3}}$ are the estimated coefficients for each independent variable. These coefficients indicate the average change in the dependent variable ${\hat{Y}}$ associated with a one-unit change in the corresponding independent variable, holding all other variables constant. The independent variables are:
-   $X_{age}$ : Age of the individual.
-   $X_{degree-score}$ : A measure of the individual's level of education or degree.
-   $X_{finance-score}$ : A measure of the individual's financial stability or status.
-   $X_{health-score}$ : A measure of the individual's overall health.
-   $X_{divorce-score}$ : A measure of the individual's likelihood of divorce or past divorces.
-   $X_{babies-number}$ : The number of babies/children the individual has.

The given multiple linear regression analysis aimed to predict an unspecified dependent variable based on several independent variables, including babies (intercept), finance score, health score, and two levels of happiness (not too happy and very happy). The model's overall explanatory power is quite low, with an R² of 0.009, indicating that it only accounts for 0.9% of the variation in the dependent variable.The finance and health scores both have positive relationships with the dependent variable, with coefficients of 0.03 and 0.06, respectively. The confidence intervals for these variables do not include zero, suggesting that these relationships are statistically significant. However, the coefficients for the happiness levels (not too happy and very happy) are small and have confidence intervals that include zero, which indicates that they might not be significantly related to the dependent variable.

@@

## Table of Relationship between Number of Children and Gender.

In the Table 3 ,which presented in the table indicate that the sex distribution varies depending on the number of babies in the family.Across all groups, there is a consistent pattern of a higher percentage of females compared to males. The lowest difference in sex distribution is observed among families with no babies, where the female-to-male ratio is relatively closer (54.53% female vs. 45.47% male). As the number of babies in a family increases, the percentage of females also increases, with the highest difference observed in families with 1 and 4 babies. In these groups, the sex distribution is more skewed towards females, with 60.92% and 60.98% female representation, respectively.

```{r}
#| message: false
#| echo: false
#| warning: false

sex_table <- data %>% 
  group_by(babies, sex) %>% 
  summarize(response = n(), variance = var(as.numeric(sex))) %>%
  mutate(percent = round(response/sum(response)*100, 2)) %>%
  select(babies, sex, percent) %>%
  spread(sex, percent)

kable(sex_table, caption = "Relationship between Number of Children and Gender") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
